---
title: 'Module 15 Challenge'
author: "JH"
date: "2/4/2022"
output: html_document
---

Deliverable 1: Linear Regression to Predict MPG

```{r}
library(dplyr)
```


```{r}
MechaCar_df <- read.csv(file='MechaCar_mpg.csv',check.names=F,stringsAsFactors = F)
```

Perform linear regression: pass in all six columns, and add the MechaCar dataframe

```{r}
# show df
names(MechaCar_df)
```
```{r}
#create linear model
lm(mpg ~ vehicle_length + 
     vehicle_weight + 
     spoiler_angle + 
     ground_clearance + 
     AWD + 
     mpg,data=MechaCar_df)

```
```{r}
#p-value and our r-squared
#summarize linear model
summary(lm(mpg ~ vehicle_length + 
              vehicle_weight + 
              spoiler_angle + 
              ground_clearance + 
              AWD + 
              mpg,data=MechaCar_df)) 
```

Deliverable 2: Create Visualizations for the Trip Analysis

```{r}
suspension_coil <- read.csv(file='Suspension_Coil.csv',check.names=F,stringsAsFactors = F)
```

```{r}
names(suspension_coil)
```

total_summary dataframe using the summarize() function to get the mean, median, variance, and standard deviation of the suspension coil’s PSI column

```{r}
total_summary <- suspension_coil %>% 
                summarize( Mean=mean(PSI), Median=median(PSI), Variance=var(PSI), SD=sd(PSI), .groups = 'keep')

```


```{r}
lot_summary <- suspension_coil %>%
                group_by(Manufacturing_Lot) %>% 
                summarize( Mean=mean(PSI), Median=median(PSI), Variance=var(PSI), SD=sd(PSI), .groups = 'keep')

```


Deliverable 3: T-Tests on Suspension Coils 

```{r}
# determine if the PSI across all manufacturing lots
# is statistically different from the population mean of 1,500
# mu=1500
# names(suspension_coil)

PSI_manufacturing_lots <- t.test(suspension_coil$PSI, mu=1500)
show(PSI_manufacturing_lots)
```

Use the t.test() function and subset() to determine if the PSI for each manufacturing lot is statistically different from the population mean of 1,500 

```{r}
lot1 <- t.test(subset(suspension_coil_df, Manufacturing_Lot == "Lot1")$PSI, mu=1500)
show(lot1)
```


```{r}
lot2 <- t.test(subset(suspension_coil_df, Manufacturing_Lot == "Lot2")$PSI, mu=1500)
show(lot2)
```

```{r}
lot3 <- t.test(subset(suspension_coil_df, Manufacturing_Lot == "Lot3")$PSI, mu=1500)
show(lot3)
```



